Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-09-03 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:09:02	21:34:49	(Wed 2.Sep)
la2pdf commit - 2015:09:03	08:37:55	(Thu 3.Sep)
la2pdf commit - 2015:09:03	11:31:05	(Thu 3.Sep)

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/cross.jpg}%
\caption{The cross and accompanying anchor used to test the beamformers.}\label{windows_steering}
\end{figure}

@@

@@

Two different scenes will be presented. One of the 1500 DWT oil tanker wreck Holmengraa lying at a slanted seabed at 77\;m depth outside of Horten, Norway~\cite{holmengraa}. It measures 68\;m by 9\;m and fills most of the highlighted sector. The other scene is of an iron cross connected to a an anchor (fig ???).

>>>>

\begin{figure}[tbp]%
\includegraphics[width=\linewidth]{gfx/cross.jpg}%
\caption{The cross and accompanying anchor used to test the beamformers.}\label{cross}
\end{figure}

@@

The window database we will construct will contain $N_\beta$ Kaiser windows with unique $\beta$-values, each being steered in $N_\phi$ different directions. This gives us $N_w = N_\beta N_\phi$ unique windows.

@@

Two different scenes will be presented. One of the 1500 DWT oil tanker wreck Holmengraa lying at a slanted seabed at 77\;m depth outside of Horten, Norway~\cite{holmengraa}. It measures 68\;m by 9\;m and fills most of the highlighted sector. The other scene is of an iron cross connected to a an anchor (\Fig{cross}).
